\LARGE \bf Human-Robot Interaction: Tackling the AI Challenges

### 2014-04-22 paper.tex
'Small' corrections from reviewer 2

This lead to a bidirectional design process: from \emph{bottom-up} regarding
the choices of concepts to model, \emph{top-down} regarding the upper part of the
taxonomy. This upper part of the ontology is pictured on
Figure~\ref{fig|upper_tbox}. All the classes visible on this figure belong to the
{\sc OpenCyc} namespace (the {\tt cyc:} prefix is omitted for clarity).

@@

The definition of the \concept{Bottle} is a case in point:

@@

The system supports quantification (``give me \{a | the | some | all | any |
...\} can''), thematic roles (action-specific predicates that qualify the
actions), interactive disambiguation (the robot asks questions when it needs
more information), anaphora resolution (``give \emph{it} to me'') based on
dialogue history. It also permits knowledge extension by learning new semantic
structures (for instance, a sentence like ``learn that cats are animals'' is
converted into \stmt{Cat subClassOf Animal} and added to the knowledge base),
interprets common temporal and place adverbs (like \emph{above} or
\emph{tomorrow}) and translates to a certain extend \emph{states} (``I'm
tired'') into \emph{experiences} (\stmt{HUMAN experiences state\_1, state\_1
hasFeature tired}).

@@

Another example, when the human says ``this'', the robot checks if the human is
currently pointing at some object. In that case, \emph{this} is replaced by the
object focused on.

Note that, while the system benefits from the complementary modalities, they
are not all required. The dialogue system can run with only the verbal
modality, at the cost of a simpler interaction.

The second level of integration of multi-modality is implicit: by computing
symbolic properties from the geometry, richer descriptions and hence
discrimination possibilities are available: for instance, if reachability is
available, the robot may ask ``do you mean the bottle that is accessible to
me?'' to discriminate between the three bottles. That way, procedures relying
on discrimination transparently benefit from added modalities (we kindly refer
the interested readers to~\cite{Ros2010b} for a detailed account of our
approach to interactive concept discrimination with the accompanying algorithms).

@@

While parts of the architecture (SPARK, ORO) have been deployed with external
execution controllers (like {\sc Cram}~\cite{Beetz2010} or the BERT
platform~\cite{Lallee2010b}, as reported in~\cite{Lemaignan2010}), we have also
developed dedicated robot controllers which integrate the whole stack introduced
on Figure~\ref{fig|archi}. {\sc Shary}~\cite{clodic2008shary} is the main one,
written in the PRS~\cite{Ingrand1996} language. We also use the Python-based
{\sc pyRobots} collection of tools that provide a large set of high-level
actions and an event-based architecture well suited for prototyping.

@@

This experiment involved a more complex decisional layer where the ORO server
was used in conjunction with the HATP symbolic task planner and the {\sc Shary}
execution controller (the complete software architecture we deployed for this
experiment is the one pictured on Figure~\ref{fig|archi},
page~\pageref{fig|archi}).

>>>>

This leads to a bidirectional design process: from \emph{bottom-up} regarding
the choices of concepts to model, \emph{top-down} regarding the upper part of the
taxonomy. This upper part of the ontology is pictured on
Figure~\ref{fig|upper_tbox}. All the classes visible in this figure belong to the
{\sc OpenCyc} namespace (the {\tt cyc:} prefix is omitted for clarity).

@@

The definition of the \concept{Bottle} is a typical example:

@@

The system supports quantification (``give me \{a | the | some | all | any |
...\} can''), thematic roles (action-specific predicates that qualify the
actions), interactive disambiguation (the robot asks questions when it needs
more information), anaphora resolution (``give \emph{it} to me'') based on
dialogue history. It also permits knowledge extension by learning new semantic
structures (for instance, a sentence like ``learn that cats are animals'' is
converted into \stmt{Cat subClassOf Animal} and added to the knowledge base
after checking for possible contradictions with existing knowledge),
interprets common temporal and place adverbs (like \emph{above} or
\emph{tomorrow}) and translates to a certain extend \emph{states} (``I'm
tired'') into \emph{experiences} (\stmt{HUMAN experiences state\_1, state\_1
hasFeature tired}). We kindly refer the readers to~\cite{Lemaignan2011a} for a
complete discussion of these capabilities and the related algorithms.

@@

Another example, when the human says ``this'', the robot checks if the human is
currently pointing at some object. In that case, \emph{this} is replaced by the
object focused on. Otherwise, the robot performs a lookup in the dialogue history
to find a previous concept that the user could refer to (anaphora resolution).

Note that, while the system benefits from the complementary modalities, they are
not all required. The dialogue system can run with the verbal modality alone, at
the cost of a simpler interaction: if the human says ``this'' without the robot
tracking what the human points at, no \stmt{HUMAN pointsAt ...} fact is
available in the knowledge base, and the robot fallbacks on the anaphora
resolution step alone.

The second level of integration of multi-modality is implicit. By continuously
computing symbolic properties from the geometric model, richer descriptions and
hence discrimination possibilities are available. For instance, the robot may
compute that one bottle is next to a glass while another one stands alone, and
these symbolic descriptions are transparently re-used in a dialogue context to
generate unambiguous references to discriminate between similar objects: ``do
you mean the bottle that is next to the glass?'' (we kindly refer the interested
readers to~\cite{Ros2010b} for a detailed account of our approach to interactive
concept discrimination, along with the related algorithms).

@@

While parts of the architecture (SPARK, ORO) have been deployed with external
execution controllers (like {\sc Cram}~\cite{Beetz2010} or the BERT
platform~\cite{Lallee2010b}, as reported in~\cite{Lemaignan2010}), we have also
developed dedicated robot controllers which integrate the whole stack introduced
in Figure~\ref{fig|archi}. {\sc Shary}~\cite{clodic2008shary} is the main one,
written in the PRS~\cite{Ingrand1996} language. We also use the Python-based
{\sc pyRobots} collection of tools that provide a large set of high-level
actions and an event-based architecture well suited for prototyping.

@@

This experiment involved a more complex decisional layer where the ORO server
was used in conjunction with the HATP symbolic task planner and the {\sc Shary}
execution controller (the complete software architecture we deployed for this
experiment is the one pictured in Figure~\ref{fig|archi},
page~\pageref{fig|archi}).
